### 2024-12-05 draft.tex
Done draft ideas

\section*{Draft ideas}
\subsection{Introduction}
\cite{tian2022assumption}
\cite{qasim2016formalization}

\subsubsection{Motivation}
\begin{itemize}
    \item Enriching the HOL4 Theory Library
    \item Supporting Future Applications
    \item Providing Analytical Tools
\end{itemize}

@@

\subsubsection{Results}
\begin{itemize}
    \item \textbf{Lyapunov CLT}: For independent random variables \(X_1, X_2, \ldots, X_n \) with finite means, variances, and third moments, if the Lyapunov condition is satisfied:
$$
\frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty,
$$
then the normalized sum \( \frac{S_n - \mu}{s_n} \) converges in distribution to the standard normal distribution \( N(0, 1) \).
    \item \textbf{Proof}: It establishes that
    \begin{itemize}
        \item Error bounds of the test function \(f\) by Taylor expansion and moment inequalities.
        \item Asymptotic vanishing of higher-order terms under the Lyapunov condition.  \item A rigorous comparison between the distribution of \( \frac{S_n}{s_n} \) and \( N(0, 1)\), bounded by \( O\left(\frac{\Gamma_n}{s_n^3}\right) \).
    \end{itemize}

These results illustrate the robustness of the Lyapunov CLT against heterogeneous distributions and, in fact, form a bridge between classical formulations and modern applications.
\end{itemize}

\subsection{Background and Related Works}
\subsubsection{Background}
Different versions of CLT \cite{fischer2011history}
\begin{itemize}
    \item \textbf{Classical Central Limit Theorem} \cite{ross2019first}
    \begin{itemize}
        \item \textbf{Proven by:} De Moivre, Laplace
        \item \textbf{Statement:} If \( X_1, X_2, \ldots, X_n \) are independent and identically distributed (i.i.d.) random variables with finite mean \( \mu \) and variance \( \sigma^2 \), then:
  \[
  Z_n = \frac{\sum_{i=1}^n X_i - n\mu}{\sigma\sqrt{n} } \xrightarrow{d} N(0, 1).
  \]
  \item \textbf{Significance:} Foundation of probability theory and statistics, used in inferential statistics, e.g., hypothesis testing and confidence intervals.
    \end{itemize}

@@

\textbf{Isabelle/HOL's Formalization of the CLT}
In Isabelle/HOL, the CLT has been formalized in a powerful and especially elegant way using the \textbf{characteristic function approach}, which relies on the fact that characteristic functions uniquely determine probability distributions and their pointwise convergence implies convergence in distribution.

@@

\subsection{Premilaires}
\subsubsection{HOL4}
\cite{tian2022assumption}
\subsubsection{Measure Theory}
\cite{qasim2016formalization}
\subsubsection{Lebesgue Integration Theory}
\cite{qasim2016formalization}
\subsubsection{Probability Theory}
\cite{qasim2016formalization}

\newpage
\subsection{Central Limit Theorem}
Informal proof of Lyapounov's theorem for a single sequence by the method of Lindeberg \cite{chung2000course}.
\begin{itemize}
    \item \textbf{Notation and Statement}
    \begin{enumerate}
    \item \( \{X_j\}_{j=1}^n \) be a sequence of independent random variables with:
    \begin{itemize}
        \item[] \( \mathbb{E}[X_j] = 0 \), 
        \item[] \( \text{Var}(X_j) = \sigma_j^2 \) (finite variances, \( \sigma_j^2 < \infty \)),
        \item[] \( \mathbb{E}[|X_j|^3] = \gamma_j \) (finite third moments, \( \gamma_j < \infty \)).
    \end{itemize}

@@

        \item Statement:
    If 
    \[
   \frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty
   \]
   then 
   \[
   \frac{S_n}{s_n} \xrightarrow{d} \Phi
   \]
   where \( \Phi\) denotes the standard normal distribution \( \mathcal{N}(0,1) \).

@@

Since  \( Y_j \sim \mathcal{N}(0, \sigma_j^2) \), the normalized random variable:
\[
\frac{Y_j}{s_n} \sim \mathcal{N}\left(0, \frac{\sigma_j^2}{s_n^2}\right)
\]

@@

Now, construct the sequence \( Z\):
\[
Z_j = Y_1 + \dots + Y_{j-1} + X_j + \dots + X_n, \quad 1 \leq j \leq n
\]
Thus:
\begin{itemize}
    \item[] \( Z_1 = X_2 + X_3 + \dots + X_n \),
    \item[] \( Z_2 = Y_1 + X_3 + \dots + X_n \),
    \item[] \( Z_n = Y_1 + Y_2 + \dots + Y_{n-1} \)
\end{itemize}

Each \( Z_j \) represents a sum that is partially replaced. All variables before \( X_j \) are replaced by \( Y_j \), but the variable after \( X_j \) remains as \( X_j \).

@@

By telescoping:
\[
\mathbb{E}\left[f\left(\frac{S_n}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Z_n}{s_n}\right)\right] = \sum_{j=1}^n \left[\mathbb{E}\left[f\left(\frac{X_j + Z_j}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Y_j + Z_{j+1}}{s_n}\right)\right]\right]
\]

\item \textbf{Taylor Expansion of \( f \)}

@@

Then, substitute with:
\begin{itemize}
    \item \( \xi = Z_j / s_n \),
    \item \( \eta = X_j / s_n \),
    \item \( \zeta = Y_j / s_n \).
\end{itemize}
We have:
   \begin{equation} \label{eq:1}
       \left| \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{X_j}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{Y_j}{s_n}\right)\right] \right| \leq \frac{M}{6} \left( \mathbb{E}\left[\left| \frac{X_j}{s_n} \right|^3\right] + \mathbb{E}\left[\left| \frac{Y_j}{s_n} \right|^3\right] \right)
   \end{equation}

\item \textbf{Error Bound Using Lyapunov's Condition}

@@

Since \( \mathbb{E}[|X_j|^3] = \gamma_j \) and \(\mathbb{E}[|Y_j|^3] = c \sigma_j^3\), we wrire:
     \[
   \mathbb{E}\left[\left|\frac{X_j}{s_n}\right|^3\right] + \mathbb{E}\left[\left|\frac{Y_j}{s_n}\right|^3\right] = \frac{\gamma_j}{s_n^3} + \frac{c \sigma_j^3}{s_n^3}
   \]

By summing over \(j = 1, \dots , n\), \eqref{eq:1} becomes:
\[
\sum_{j=1}^n \left| \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{X_j}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{Y_j}{s_n}\right)\right] \right| \leq \frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \sigma_j^3}{s_n^3} \right)
\]

@@

\begin{equation} \label{eq:2}
\frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \cdot \sigma_j^3}{s_n^3} \right) \leq \frac{M}{6} \cdot \frac{1}{s_n^3} \sum_{j=1}^n (1 + c) \gamma_j
\end{equation}

Let \( K = \frac{M}{6}(1 + c) \), and the total third absolute moment of \( X_j \):
\[
\Gamma_n = \sum_{j=1}^n \gamma_j ( \space as \space define \space above)
\]
We substitute these into the inequality \eqref{eq:2}:
\begin{equation} \label{eq:3}
\frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \cdot \sigma_j^3}{s_n^3} \right) \leq K \cdot \frac{\Gamma_n}{s_n^3}
\end{equation}

By the definition of Big-O Notation, we have 
\begin{displayquote}
For a function \( f(n) \), we say that \( f(n) = O(g(n)) \) if there exist positive constants \( C > 0 \) and \( n_0 \geq 1 \) such that:
\[
|f(n)| \leq C |g(n)|, \quad \text{for all } n \geq n_0
\]
\end{displayquote}

Here:
\begin{itemize}
    \item \( f(n) = \frac{\Gamma_n}{s_n^3} \),
    \item \( g(n) = \frac{\Gamma_n}{s_n^3} \)
\end{itemize}

Clearly:
\[
|f(n)| = \left| \frac{\Gamma_n}{s_n^3} \right| \quad \text{and} \quad |g(n)| = \left| \frac{\Gamma_n}{s_n^3} \right|
\]

Since \( f(n) \) and \( g(n) \) are identical, we have:
\[
|f(n)| \leq 1 \cdot |g(n)| \quad \text{for all } n \geq 1
\]

@@

Since we have found constants \( C = 1 \) and \( n_0 = 1 \) such that:
\[
|f(n)| \leq C |g(n)| \quad \text{for all } n \geq n_0,
\]
it follows by the definition of Big-O notation that:
\begin{equation} \label{eq:4}
\frac{\Gamma_n}{s_n^3} = O\left(\frac{\Gamma_n}{s_n^3}\right)
\end{equation}

The Big O Notation property called \textbf{Multiplication by a constant} states that:
Let \( k \) be a nonzero constant. Then:
\[
O(|k| \cdot g) = O(g)
\]
Apply this to \eqref{eq:4}, we have:
   \[
   K \cdot \frac{\Gamma_n}{s_n^3} = O\left(\frac{\Gamma_n}{s_n^3}\right)
   \]
Then \eqref{eq:3} becomes:
\[
\frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \cdot \sigma_j^3}{s_n^3} \right) \leq O\left(\frac{\Gamma_n}{s_n^3}\right)
\]

We have thus obtained the following estimate:
\[
\forall f \in C^3: \left| \space  \mathbb{E}\left[f\left(\frac{S_n}{s_n}\right)\right] - \mathbb{E}\left[f\left(N\right)\right] \right| \leq O\left(\frac{\Gamma_n}{s_n^3}\right) 
\]

@@

By Lyapunov's condition:
\[
\frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty
\]
This directly implies that:
\[
\left| \mathbb{E}\left[f\left(\frac{S_n}{s_n}\right)\right] - \mathbb{E}\left[f(N)\right] \right| \to 0.
\]

Since \( \mathbb{E}[f(S_n / s_n)] \to \mathbb{E}[f(N)] \) for all bounded and continuous test functions \( f \), by the general criterion for vague convergence, we conclude that:
\[
\frac{S_n}{s_n} \xrightarrow{d} \mathcal{N}(0, 1)
\]

@@

@@

\subsubsection{Future Directions}
...

>>>>

\section*{Draft ideas}
\subsection{Abstract}
\begin{itemize}
    \item What is the CLT? Why is formal verification important?
    \item What limitations or gaps does this work address?
    \item Briefly summarize the methods, results, and significance.
\end{itemize}

\subsection{Introduction}
\cite{tian2022assumption}
\cite{qasim2016formalization}
\begin{itemize}
    \item What is CLT
    \item Define the CLT in its simplest form (e.g., i.i.d. random variables)
    \item Highlight its importance in statistics, machine learning, and other fields as a foundation for normal approximation.
\end{itemize}

\subsubsection{Motivation}
Why formalize the CLT in HOL4? 
The challenges with probabilistic reasoning, the need for rigor, and the importance of verifying a key theorem like the CLT.
\begin{itemize}
    \item Enriching the HOL4 Theory Library
    \item Supporting Future Applications
    \item Providing Analytical Tools
\end{itemize}

@@

\subsubsection{Results}
This form of CLT is more general than the i.i.d case but not the most general (not the Lindeberg-Feller version).

\begin{itemize}
    \item \textbf{Lyapunov CLT}: For independent random variables \(X_1, X_2, \ldots, X_n \) with finite means, variances, and third moments, if the Lyapunov condition is satisfied:
$$
\frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty,
$$
then the normalized sum \( \frac{S_n - \mu}{s_n} \) converges in distribution to the standard normal distribution \( N(0, 1) \).
    \item \textbf{Proof}: It establishes that
    \begin{itemize}
        \item Error bounds of the test function \(f\) by Taylor expansion and moment inequalities.
        \item Asymptotic vanishing of higher-order terms under the Lyapunov condition.  \item A rigorous comparison between the distribution of \( \frac{S_n}{s_n} \) and \( N(0, 1)\), bounded by \( O\left(\frac{\Gamma_n}{s_n^3}\right) \).
    \end{itemize}

These results illustrate the robustness of the Lyapunov CLT against heterogeneous distributions and, in fact, form a bridge between classical formulations and modern applications.

Also, highlight key formal results of other lemmas and theorems to support (e.g., bounding errors using Big-O, weak convergence).
\end{itemize}

\subsection{Background and Related Works}
\subsubsection{Historical Background}
Introduce the histrory of CLT and mention different versions of CLT \cite{fischer2011history}
\begin{itemize}
    \item Classical versions: De Moivre-Laplace (i.i.d.), Lindeberg-Feller, Lyapunov’s theorem.
    \item Explain why Lyapunov’s version is chosen (finite moments, no characteristic functions).
\end{itemize}

\begin{itemize}
    \item \textbf{Classical Central Limit Theorem} \cite{ross2019first}
    \begin{itemize}
        \item \textbf{Proven by:} De Moivre, Laplace
        \item \textbf{Statement:} If \( X_1, X_2, \ldots, X_n \) are independent and identically distributed (i.i.d.) random variables with finite mean \( \mu \) and variance \( \sigma^2 \), then:
  \[
  Z_n = \frac{\sum_{i=1}^n X_i - n\mu}{\sigma\sqrt{n} } \xrightarrow{d} N(0, 1).
  \]
  \item \textbf{Significance:} Foundation of probability theory and statistics, used in inferential statistics, e.g., hypothesis testing and confidence intervals.
    \end{itemize}

@@

\textbf{Isabelle/HOL's Formalization of the CLT}
In Isabelle/HOL, the CLT has been formalized in a powerful and especially elegant way using the \textbf{characteristic function approach}, which relies on the fact that characteristic functions uniquely determine probability distributions and their pointwise convergence implies convergence in distribution.
\cite{serafin2015formally}

@@

\subsubsection{Overview of Informal Proof}
\begin{itemize}
    \item Highlight the direct and real-valued approach of Lyapunov's proof.
    \item Discuss how it avoids characteristic functions and instead uses bounding error terms (Taylor expansion, Big-O).
\end{itemize}

\subsection{Preliminaries}
\subsubsection{HOL4}
\cite{tian2022assumption}
\subsubsection{Measure Theory}
\cite{qasim2016formalization}
\subsubsection{Lebesgue Integration Theory}
\cite{qasim2016formalization}
\subsubsection{Probability Theory}
\cite{qasim2016formalization}

\newpage
\subsection{The proof of Central Limit Theorem}
\subsubsection{Informal Proof}
Informal proof of Lyapounov's theorem for a single sequence by the method of Lindeberg \cite{chung2000course}.
\begin{itemize}
    \item \textbf{Notation and Statement}
    \begin{enumerate}
    \item \( \{X_j\}_{j=1}^n \) be a sequence of independent random variables with:
    \begin{itemize}
        \item[] \( \mathbb{E}[X_j] = 0 \), 
        \item[] \( \text{Var}(X_j) = \sigma_j^2 \) (finite variances, \( \sigma_j^2 < \infty \)),
        \item[] \( \mathbb{E}[|X_j|^3] = \gamma_j \) (finite third moments, \( \gamma_j < \infty \)).
    \end{itemize}

@@

        \item Statement:
    If 
    \[
   \frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty.
   \]
   then 
   \[
   \frac{S_n}{s_n} \xrightarrow{d} \Phi
   \]
   where \( \Phi\) denotes the standard normal distribution \( \mathcal{N}(0,1) \).

@@

Since  \( Y_j \sim \mathcal{N}(0, \sigma_j^2) \), the normalized random variable:
\[
\frac{Y_j}{s_n} \sim \mathcal{N}\left(0, \frac{\sigma_j^2}{s_n^2}\right).
\]

@@

Now, construct the sequence \( Z\):
\[
Z_j = Y_1 + \dots + Y_{j-1} + X_{j + 1} + \dots + X_n, \quad 1 \leq j \leq n.
\]
Thus:
\begin{itemize}
    \item[] \( Z_1 = X_2 + X_3 + \dots + X_n \),
    \item[] \( Z_2 = Y_1 + X_3 + \dots + X_n \),
    \item[] \( Z_n = Y_1 + Y_2 + \dots + Y_{n-1} \).
\end{itemize}

In general, each \( Z_j \) represents a sum where:
\begin{itemize}
    \item All variables before \( X_j \) are replaced by \( Y_1, \dots, Y_{j-1} \),
    \item \( X_j \) is excluded from the summation,
    \item All variables after \( X_j \) remain as \( X_{j+1}, X_{j+2}, \dots, X_n \).
\end{itemize}

Thus, by telescoping property, we have:
\[
Y_j + Z_j = X_{j+1} + Z_{j+1}.
\]

@@

By telescoping:
\[
\mathbb{E}\left[f\left(\frac{S_n}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Z_n}{s_n}\right)\right].
\]

\[
= \mathbb{E}\left[f\left(\frac{X_1 + \cdots + X_n}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Y_1 + \cdots + Y_n}{s_n}\right)\right].
\]

\[
= \sum_{j=1}^n \left[\mathbb{E}\left[f\left(\frac{X_j + Z_j}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Y_j + Z_j}{s_n}\right)\right]\right].
\]

\item \textbf{Expand expectations with Taylor’s theorem}

@@

Then, substitute with:
\begin{itemize}
    \item \( \xi = Z_j / s_n \),
    \item \( \eta = X_j / s_n \),
    \item \( \zeta = Y_j / s_n \).
\end{itemize}
We have:
   \begin{equation} \label{eq:1}
       \left| \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{X_j}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{Y_j}{s_n}\right)\right] \right| \leq \frac{M}{6} \left( \mathbb{E}\left[\left| \frac{X_j}{s_n} \right|^3\right] + \mathbb{E}\left[\left| \frac{Y_j}{s_n} \right|^3\right] \right).
   \end{equation}

\item \textbf{Bound error terms using Big-O notation}

@@

Since \( \mathbb{E}[|X_j|^3] = \gamma_j \) and \(\mathbb{E}[|Y_j|^3] = c \sigma_j^3\), we wrire:
     \[
   \mathbb{E}\left[\left|\frac{X_j}{s_n}\right|^3\right] + \mathbb{E}\left[\left|\frac{Y_j}{s_n}\right|^3\right] = \frac{\gamma_j}{s_n^3} + \frac{c \sigma_j^3}{s_n^3}.
   \]

By summing over \(j = 1, \dots , n\), \eqref{eq:1} becomes:
\[
\sum_{j=1}^n \left| \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{X_j}{s_n}\right)\right] - \mathbb{E}\left[f\left(\frac{Z_j}{s_n} + \frac{Y_j}{s_n}\right)\right] \right| \leq \frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \sigma_j^3}{s_n^3} \right).
\]

@@

\begin{equation} \label{eq:2}
\frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \cdot \sigma_j^3}{s_n^3} \right) \leq \frac{M}{6} \cdot \frac{1}{s_n^3} \sum_{j=1}^n (1 + c) \gamma_j.
\end{equation}

Let \( K = \frac{M}{6}(1 + c) \), and the total third absolute moment of \( X_j \):
\[
\Gamma_n = \sum_{j=1}^n \gamma_j ( \space as \space define \space above).
\]
We substitute these into the inequality \eqref{eq:2}:
\begin{equation} \label{eq:3}
\frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \cdot \sigma_j^3}{s_n^3} \right) \leq K \cdot \frac{\Gamma_n}{s_n^3}.
\end{equation}

By the definition of Big-O Notation, we have 
\begin{displayquote}
For a function \( f(n) \), we say that \( f(n) = O(g(n)) \) if there exist positive constants \( C > 0 \) and \( n_0 \geq 1 \) such that:
\[
|f(n)| \leq C |g(n)|, \quad \text{for all } n \geq n_0.
\]
\end{displayquote}

Here:
\begin{itemize}
    \item \( f(n) = \frac{\Gamma_n}{s_n^3} \),
    \item \( g(n) = \frac{\Gamma_n}{s_n^3} \).
\end{itemize}

Clearly:
\[
|f(n)| = \left| \frac{\Gamma_n}{s_n^3} \right| \quad \text{and} \quad |g(n)| = \left| \frac{\Gamma_n}{s_n^3} \right|.
\]

Since \( f(n) \) and \( g(n) \) are identical, we have:
\[
|f(n)| \leq 1 \cdot |g(n)| \quad \text{for all } n \geq 1.
\]

@@

Since we have found constants \( C = 1 \) and \( n_0 = 1 \) such that:
\[
|f(n)| \leq C |g(n)| \quad \text{for all } n \geq n_0,
\]
it follows by the definition of Big-O notation that:
\begin{equation} \label{eq:4}
\frac{\Gamma_n}{s_n^3} = O\left(\frac{\Gamma_n}{s_n^3}\right).
\end{equation}

The Big O Notation property called \textbf{Multiplication by a constant} states that:
Let \( k \) be a nonzero constant. Then:
\[
O(|k| \cdot g) = O(g)
\]
Apply this to \eqref{eq:4}, we have:
   \[
   K \cdot \frac{\Gamma_n}{s_n^3} = O\left(\frac{\Gamma_n}{s_n^3}\right).
   \]
Then \eqref{eq:3} becomes:
\[
\frac{M}{6} \sum_{j=1}^n \left( \frac{\gamma_j}{s_n^3} + \frac{c \cdot \sigma_j^3}{s_n^3} \right) \leq O\left(\frac{\Gamma_n}{s_n^3}\right).
\]

We have thus obtained the following estimate:
\[
\forall f \in C^3: \left| \space  \mathbb{E}\left[f\left(\frac{S_n}{s_n}\right)\right] - \mathbb{E}\left[f\left(N\right)\right] \right| \leq O\left(\frac{\Gamma_n}{s_n^3}\right).
\]

@@

By Lyapunov's condition:
\[
\frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty.
\]
This directly implies that:
\[
\left| \mathbb{E}\left[f\left(\frac{S_n}{s_n}\right)\right] - \mathbb{E}\left[f(N)\right] \right| \to 0.
\]

Since \( \mathbb{E}[f(S_n / s_n)] \to \mathbb{E}[f(N)] \) for all bounded and continuous test functions \( f \), by the general criterion for vague convergence (in Theorem 6.1.6 in \cite{chung2000course}), we conclude that:
\[
\frac{S_n}{s_n} \xrightarrow{d} \mathcal{N}(0, 1).
\]

@@

\subsubsection{Formal Proof in HOL4}
Key lemmas and theorems:
\begin{itemize}
    \item Weak convergence
    \item Taylor expansion of expectations
    \item Big-O bounds for error terms
\end{itemize}

\subsection{Limitations and Future Directions}
\subsubsection{Limitations}
\begin{itemize}
    \item Mention limitations in HOL4’s current libraries: Incomplete ComplexTheory, which prevents characteristic function-based proofs, Lack of direct support for third moments of normal random variables, making certain bounds harder to verify formally.
    \item This work is for proof of Lyapunov’s version, which is more general than the i.i.d. case but not the most general form (e.g., Lindeberg-Feller).
\end{itemize}

\subsubsection{Future Directions}
\begin{itemize}
    \item Explore the possibility of extending HOL4 to include: Characteristic functions and ComplexTheory, and A general Lindeberg-Feller version of the CLT.    
\end{itemize}

@@
